### 2018-07-03 submission/manuscript.tex
change title

\section{Assessing Differences in High Fidelity DNA Polymerase for 16S
rRNA Gene
Sequencing}\label{assessing-differences-in-high-fidelity-dna-polymerase-for-16s-rrna-gene-sequencing}

>>>>

\section{Assessing the Differences in 16S rRNA Gene Sequencing Due to
High Fidelity DNA
Polymerase}\label{assessing-the-differences-in-16s-rrna-gene-sequencing-due-to-high-fidelity-dna-polymerase}
